\begin{document}

\begin{thebibliography}{9}

  \bibitem{typewriting_behaviour}
  DVORAK, August idr. 1936. \textit{Typewriting behaviour: psychology applied to teaching and learning typewriting}.
  American Book Company

  \bibitem{arch_wiki}
  Arch Wiki: \textit{Keyboard input} [spletni vir].
  \mbox{[Citirano 12. 04. 2019]}. \\
  Dostopno na: <https://wiki.archlinux.org/index.php/Keyboard\_input>.

  \bibitem{keyboard_history}
  BELLIS, Mary. 2018. Thought Co.: \textit{The History of the Computer Keyboard} [spletni vir].
  \mbox{[Citirano 12. 02. 2019]}.
  Dostopno na: <https://www.thoughtco.com/history-of-the-computer-keyboard-1991402>.

  \bibitem{programmer_dvorak}
  KAUFMANN, Roland. 2017. \textit{Programmer Dvorak} [spletni vir].
  \mbox{[Citirano 11. 01. 2019]}.
  Dostopno na: <https://www.kaufmann.no/roland/dvorak/>.

  \bibitem{typing_effort}
  KRZYWINSKI, Martin. 2018. \textit{Carpalx - typing effort} [spletni vir].
  \mbox{[Citirano 16. 01. 2019]}.
  Dostopno na: <http://mkweb.bcgsc.ca/carpalx/?typing\_effort>.

  \bibitem{roland_mail}
  KAUFMANN, Roland. 2018. \textit{Programmer Dvorak} [elektronska pošta].
  \mbox{[Citirano 12. 04. 2019]}.
  Sporočilo za Erazma Kokota dne 22. 10. 2018.

  \bibitem{dvorak_procon}
  BROOKS, Marcus. 1999. \textit{Dvorak Pros and Cons} [spletni vir]
  \mbox{[Citirano 12. 04. 2019]}.
  Dostopno na: <http://dvorak.mwbrooks.com/procon.html>

  \bibitem{mwbrooks_opinions}
  BROOKS, Marcus. 1999. \textit{Dissenting opinions} [spletni vir]
  \mbox{[Citirano 12. 04. 2019]}.
  Dostopno na: <http://dvorak.mwbrooks.com/dissent.html\#month>

  \bibitem{udosen}
  UDOSEN, U. J\@. 2009 \textit{Evaluation and Improvement of Dvorak Keyboard Layout Using CADWORK}.
  V: Advanced Materials Research.
  DOI: 10.4028/www.scientific.net/AMR.62-64.585

  \bibitem{curse}
  DIAMOND, Jared. 1997. \textit{The Curse of QWERTY}.
  Discover Magazine, 1. April 1997.
  Dostopno na: <http://discovermagazine.com/1997/apr/thecurseofqwerty1099/>

  \bibitem{colemak}
  COLEMAN, Shai. 2006. \textit{Colemak keyboard layout} [spletni vir]
  \mbox{[Citirano 16. 01. 2019]}.
  Dostopno na: <https://colemak.com/>

  \bibitem{win_keyboard}
  Windows Applications | Microsoft Docs [spletni vir]. [s. d.]. \textit{Keyboard input}.
  \mbox{[Citirano 12. 04. 2019]}.
  Dostopno na: <https://docs.microsoft.com/en-us/windows/desktop/learnwin32/keyboard-input>

\end{thebibliography}

\end{document}